---
title: "QHCI - Assignment 2"
author: "Jonas Brunner"
date: "11.5.2021"
output: html_document
---

# Research Question
The research questions for your group are:

	RQ1: "Do overall typing speed differ between touch-typist and non-touchtypist?"

	RQ2: "How much does the result from RQ1 influenced by whether the participants type known-words or random string?"
	

### Setup
```{r, message=FALSE}
library(tidyverse)
library(dplyr)
library(lme4)
import::from(car, leveneTest, sigmaHat)
import::from(modelr, add_residuals, add_predictions)
import::from(qqplotr, stat_qq_line, stat_qq_point, stat_qq_band) 
import::from(ARTool, art, artlm, art.con)
import::from(broom.mixed,tidy)
import::from(multcomp, glht, mcp, adjusted) 


```


### Data wrangling
Read all csv files in the /log directory and parse *user_id* and *condition* from the filename of the .csv
In the end, join it together with the *participant_info.csv*

```{r, message=FALSE}
regex_parse <- "User(\\d+)_T(\\d+)_(.*).csv"

readLog <- function(fileName) {
    csv_data <- read_csv(str_c('./log/',fileName)) %>% 
      mutate(length = str_length(stimulus)) %>% 
      group_by(stimulus_index) %>% 
      summarise(wpm = (as.double(max(length)-1)/5)/ as.double(max(input_time_ms)) * 60000, length = max(length)) %>% 
      mutate(user_id = as.numeric(str_replace(fileName, regex_parse, "\\1")), condition = str_replace(fileName, regex_parse, "\\3"))
    return(csv_data)
}

participant_info <- read_csv('./participant_info.csv')
log_files <- list.files('./log')

data <- as_tibble_col(lapply(log_files, readLog), col='nested') %>% 
        unnest(nested) %>% merge(y=participant_info, by='user_id', all.x = TRUE ) %>% 
        mutate(typing_style = if_else(is_touchtypist, 'Non-touchtypist', 'Touchtypist')) %>% 
        select(-is_touchtypist, -length)

data_with_cond <- data %>% mutate(condition = factor(condition, levels = c("Sentences", "Mix", "Random")), typing_style = factor(typing_style, levels = c("Non-touchtypist", "Touchtypist")))



```

# RQ 1
## Inspect Data
When plotting the data in a violin plot, we can not see a significant difference in WPM between 
the different typing styles.
```{r}
 data %>% 
  ggplot(aes(x = typing_style)) +
  geom_violin(aes(y = wpm), color = NA, fill = "grey") +
  geom_boxplot(aes(y=wpm), width=0.1) +
  labs(x = "", y = "WPM", title = "WPM per typing style")
```

## Linear Model Fitting
We fit a model with random-intercepts and random-slopes. Unfortunately, the qqplot shows that the data does not fulfill normality of errors.
```{r}
# m <- lmer(wpm ~ typing_style * condition + (1 | user_id), data = data_with_cond)


#This is probably not right yet
m_rep <- lmer(wpm ~ condition * typing_style + (1 + condition | user_id), data = data_with_cond)

summary(m_rep)

anova(m_rep)

shapiro.test(residuals(m_rep))

data_with_cond %>% add_predictions(m_rep) %>% add_residuals(m_rep) %>% ggplot(aes(x=pred)) + geom_hline(yintercept = 0, color="red") + geom_point(aes(y=resid))

data_with_cond %>% 
  add_residuals(m_rep) %>%
  ggplot(aes(sample = resid)) +
  stat_qq_band() +
  stat_qq_line() +
  stat_qq_point(alpha = 0.3)



```

We try to log transform the model to fulfill normality => makes it even worse

```{r}
m_log <- lmer(log(wpm) ~ condition * typing_style + (1 + condition | user_id), data = data_with_cond)

data_with_cond %>% 
  add_residuals(m_log) %>%
  ggplot(aes(sample = resid)) +
  stat_qq_band() +
  stat_qq_line() +
  stat_qq_point(alpha = 0.3)


```

We use GLHT with the untransformed model, but no significant p value is reached.
```{r}

m_rep %>% 
  glht(mcp(typing_style = "Tukey")) %>% 
  tidy(conf.int = TRUE)

m_rep %>% 
  glht(mcp(typing_style = "Tukey")) %>% 
  summary(test = adjusted("holm")) %>%
  tidy()

```



# RQ2
## Inspect Data
Out of the three conditions, Sentences results in the highest WPM
```{r}

 data %>% 
  ggplot(aes(x = condition)) +
  geom_violin(aes(y = wpm), color = NA, fill = "grey") +
  geom_boxplot(aes(y=wpm), width=0.1) +
  labs(x = "", y = "WPM", title = "WPM per Condition")

```


## Fit linear models
```{r}

m_rep <- lmer(wpm ~ condition * typing_style + (1 + condition | user_id), data = data_with_cond)

m_glht <- m_rep %>% 
  glht(mcp(condition = c(
    "(Random - Mix)/2 - Sentences = 0",
     "Random - Mix = 0"
  ))) %>% 
  summary(test = adjusted("holm"))

m_glht %>% confint() %>%  tidy()
m_glht %>% tidy()

shapiro.test(residuals(m_rep))

leveneTest(residuals(m_rep) ~ data$typing_style, center = "median")

m_rep %>%
  tidy(conf.int = TRUE) %>% 
  select(term, estimate, conf.low, conf.high) %>% 
  ggplot(aes(x = term, y = estimate, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, color = "blue") +
  coord_flip()


```


