---
title: "Project2_McCants"
author: "Taylor McCants"
date: "14/5/2021"
output: html_document
---


## Setup ##

```{r, results='hide', message=FALSE,  warning=FALSE}
# load the packages
library(tidyverse)
library(lme4)
library(ggplot2)
library(broom.mixed)
library(lmerTest)  
library(plyr)
library(lsm)
library(car)
library(stringr)
additional_packages <- c("multcomp", "PearsonDS", "ARTool", "qqplotr", "psych", "moments")
install.packages(setdiff(additional_packages, rownames(installed.packages())))  
import::from(moments, skewness)
import::from(MASS,mvrnorm)
import::from(broom.mixed,tidy)
import::from(multcomp, glht, mcp, adjusted) 
import::from(PearsonDS, rpearson)                                   
import::from(ARTool, art, artlm, art.con)                  
import::from(qqplotr, stat_qq_line, stat_qq_point, stat_qq_band) 
import::from(psych, d.ci) 
import::from(cowplot, plot_grid) 
import::from(modelr, add_residuals, add_predictions)     
import::from(car, leveneTest, sigmaHat)
```

***

## Data Processing ##

Read the data files.

```{r, message=FALSE}
# Regular expression to help parse the log files
regex_parse <- "User(\\d+)_T(\\d+)_(.*).csv"

# helper function to read in log files
read_log_files <- function(fileName){
  csv_data <- read_csv(str_c('./log/',fileName)) %>% 
      mutate(length = str_length(stimulus)) %>% 
      group_by(stimulus_index) %>% 
      summarise(wpm = (as.double(max(length)-1)/5)/ as.double(max(input_time_ms)) * 60000, length = max(length)) %>% 
      mutate(user_id = as.numeric(str_replace(fileName, regex_parse, "\\1")), condition = str_replace(fileName, regex_parse, "\\3"))
    return(csv_data)
}
# list of all log files
log_files <- list.files('./log')

# file that includes the participant information
participant_info <- read_csv("participant_info.csv")

# backup file that is already processed
combined_log_background <- read_csv(("combined_log_background.csv"))

# data wrangling
data <- as_tibble_col(lapply(log_files, read_log_files), col='nested') %>% 
        unnest(nested) %>% merge(y=participant_info, by='user_id', all.x = TRUE ) %>% 
        mutate(typing_style = if_else(is_touchtypist, 'Non-touchtypist', 'Touchtypist')) %>% 
        select(-is_touchtypist, -length)

# ? TODO add comment
data_with_cond <- data %>% mutate(condition = factor(condition, levels = c("Sentences", "Mix", "Random")), typing_style = factor(typing_style, levels = c("Non-touchtypist", "Touchtypist")))
```


## Data Exploration and Description

Overview of data:
```{r, echo=FALSE}
head(data)
```
```{r, echo=FALSE}
str(data)
```


### Visualize Descriptive Statisctics 

Summary of the data

```{r, echo=FALSE}
summary(data)
```
Violin plot that includes boxplots for *words per minute (wpm)* by the *typing styles* of users.

```{r, echo=FALSE}
# violin plot including boxplots displaying words per minute (wpm) for the two typing styles
data %>% 
  ggplot(aes(x=typing_style, y=wpm, fill=typing_style)) + 
    geom_violin() + 
    geom_boxplot(width=0.1) +
    scale_fill_brewer(palette="PuRd") + 
    theme_minimal() +
    labs(title="Words per Minute per Typing Style",x="Typing Style", y = "Words Per Minute (WPM)") +
    guides(fill=guide_legend(title="Typing Style"))
```

Based on the graph above, there is not much difference between the two *typing styles* with regards to *words per minutes (wpm)*. The same is shown in the numbers table above.

**Non-Parametric Statistics**

```{r, echo=FALSE}
# median of wpm per typing style
median_wpm_by_typing_style <- by(data = data$wpm, INDICES = data$typing_style, FUN = median) %>%
  rbind() %>%
  as_tibble()

# min of wpm per typing style
min_wpm_by_typing_style <- by(data = data$wpm, INDICES = data$typing_style, FUN = min) %>%
  rbind() %>%
  as_tibble()

# max of wpm per typing style
max_wpm_by_typing_style <- by(data = data$wpm, INDICES = data$typing_style, FUN = max) %>%
  rbind() %>%
  as_tibble()

# IQR of wpm per typing style
iqr_wpm_by_typing_style <- by(data = data$wpm, INDICES = data$typing_style, FUN = IQR) %>%
  rbind() %>%
  as_tibble()
```


* Median: Nontouchtypist = `r median_wpm_by_typing_style[[1]]` *wpms*, Touchtypist = `r median_wpm_by_typing_style[[2]]` *wpms*
* Interval: Nontouchtypist = (min= `r min_wpm_by_typing_style[[1]]` *wpms*, max=`r max_wpm_by_typing_style[[1]]` *wpms*), Touchtypist = (min=`r min_wpm_by_typing_style[[2]]` *wpms*, max=`r max_wpm_by_typing_style[[2]]` *wpms*)
* Interquartile Range (IQR) : The `IQR` of Nontouchtypists = `r iqr_wpm_by_typing_style[[1]]` and Touchtypists = `r iqr_wpm_by_typing_style[[2]]`.

The differences in median, interval, and IQR is very small, further showing that there is not a significant difference in the results from Nontouchtypist and Touchtypist.

**Parametric Statistics**

```{r, echo=FALSE}
# mean of wpm per typing style
mean_wpm_by_typing_style <- by(data = data$wpm, INDICES = data$typing_style, FUN = mean) %>%
  rbind() %>%
  as_tibble()

# variation of wpm per typing style
var_wpm_by_typing_style <- by(data = data$wpm, INDICES = data$typing_style, FUN = var) %>%
  rbind() %>%
  as_tibble()

# standard deviation of wpm per typing style
sd_wpm_by_typing_style <- by(data = data$wpm, INDICES = data$typing_style, FUN = sd) %>%
  rbind() %>%
  as_tibble()
```


* Mean: `r colnames(mean_wpm_by_typing_style[1])` = `r mean_wpm_by_typing_style[[1]]` *wpms*, `r colnames(mean_wpm_by_typing_style[2])` = `r mean_wpm_by_typing_style[[2]]` *wpms*
* Spread: Variance of `r colnames(min_wpm_by_typing_style[1])` = `r var_wpm_by_typing_style[[1]]`, Variance of `r colnames(var_wpm_by_typing_style[2])` = `r var_wpm_by_typing_style[[2]]`.
* Standard deviation: `r colnames(sd_wpm_by_typing_style[1])` = `r sd_wpm_by_typing_style[[1]]`, `r colnames(sd_wpm_by_typing_style[2])` = `r sd_wpm_by_typing_style[[2]]`

All of the values above show that they conditions are very similar.

```{r}
# r function for skewness
by(data = data$wpm, INDICES = data$typing_style, FUN = skewness)
```




#### **RQ2 - words per minute (wpm) by condition**

With RQ2 in mind we create the same plot again for *words per minute (wpm)* by the different *conditions*.

```{r, echo=FALSE, warning=FALSE}
# violin plot including boxplots displaying words per minute (wpm) for the three conditions
data %>% 
 ggplot(aes(x=condition, y=wpm, fill=condition)) + 
  geom_violin() + 
  geom_boxplot(width=0.1) +
  scale_fill_brewer(palette="PuRd") + 
  theme_minimal() +
  labs(title="Words Per Minute (WPM) by Condition",x="Condition", y = "Words Per Minute (WPM)") +
  guides(fill=guide_legend(title="Condition"))
```

In contrast to the visualization before, in this case we immediately see that the violin and boxplots appear quite different with regards to the *conditions* and *word per minutes (wpm)*.


**Non-Parametric Statistics**

```{r, echo=FALSE}
# median of wpm per typing style
median_wpm_by_condition <- by(data = data$wpm, INDICES = data$condition, FUN = median) %>%
  rbind() %>%
  as_tibble()

# min of wpm per typing style
min_wpm_by_condition <- by(data = data$wpm, INDICES = data$condition, FUN = min) %>%
  rbind() %>%
  as_tibble()

# max of wpm per typing style
max_wpm_by_condition <- by(data = data$wpm, INDICES = data$condition, FUN = max) %>%
  rbind() %>%
  as_tibble()

# IQR of wpm per typing style
iqr_wpm_by_condition <- by(data = data$wpm, INDICES = data$condition, FUN = IQR) %>%
  rbind() %>%
  as_tibble()

```


* Median: `r colnames(median_wpm_by_condition[1])` = `r median_wpm_by_condition[[1]]` *wpms*, `r colnames(median_wpm_by_condition[2])` = `r median_wpm_by_condition[[2]]` *wpms*, `r colnames(median_wpm_by_condition[3])` = `r median_wpm_by_condition[[3]]` *wpms*.

* Interval: `r colnames(min_wpm_by_condition[1])` = (min=`r min_wpm_by_condition[[1]]` *wpms*, max=`r max_wpm_by_condition[[1]]` *wpms*), `r colnames(min_wpm_by_condition[2])` =(min=`r min_wpm_by_condition[[2]]` *wpms*, max=`r max_wpm_by_condition[[2]]` *wpms* ), and  `r colnames(min_wpm_by_condition[3])`=(min=`r min_wpm_by_condition[[3]]` *wpms*, max=`r max_wpm_by_condition[[3]]` *wpms*)
  
* IQR:  `r colnames(iqr_wpm_by_condition[1])` = `r iqr_wpm_by_condition[[1]]`,  `r colnames(iqr_wpm_by_condition[2])` = `r iqr_wpm_by_condition[[2]]`, `r colnames(iqr_wpm_by_condition[3])` = `r iqr_wpm_by_condition[[3]]`.



The `median`, `min`, `max`, as well as the `IQR` this time show significant differences that are also obvious in the visualizations. Upon these we can already make a statement about RQ2.


* Condition `r colnames(max_wpm_by_condition[1])`:
  + User who had to type strings in form of `r colnames(iqr_wpm_by_condition[1])` were the slowest compared to the other conditions. This shows in the lowest `median` (`r `median_wpm_by_condition[[1]]`), `min`(`r min_wpm_by_condition[[1]]`) and `max` (`r max_wpm_by_condition[[1]]`) values. 
  + But these users had a very small spread which is by the  `IQR of` (`r iqr_wpm_by_condition[[1]]`) that is lower than the others.

* Condition `r colnames(max_wpm_by_condition[2])`:
  + User who had to type strings in `r colnames(iqr_wpm_by_condition[2])` form were faster than `r colnames(iqr_wpm_by_condition[1])` strings but slower than regular `r colnames(iqr_wpm_by_condition[3])`.
  + They had larger spread indicated by the `IQR of`(`r iqr_wpm_by_condition[[3]]`) but not the largest compared to the others .

* Condition `r colnames(max_wpm_by_condition[3])`:
  + User who had to type strings in form of `r colnames(iqr_wpm_by_condition[3])` were the fastest, which is shown in the highest `median`  (`r median_wpm_by_condition[[3]]`), `min`(`r min_wpm_by_condition[[3]]`) and `max` (`r max_wpm_by_condition[[3]]`) values compared to the other conditions. 
  + Also they had the largest spread indicated by the `IQR of`(`r iqr_wpm_by_condition[[3]]`) that is higher than the others. 
  
At this point we can already say that there are obvious differences between the *conditions*.


**Parametric Statistics**

```{r, echo=FALSE}
# mean of wpm per typing style
mean_wpm_by_condition <- by(data = data$wpm, INDICES = data$condition, FUN = mean) %>%
  rbind() %>%
  as_tibble()

# variation of wpm per typing style
var_wpm_by_condition <- by(data = data$wpm, INDICES = data$condition, FUN = var) %>%
  rbind() %>%
  as_tibble()

# standard deviation of wpm per typing style
sd_wpm_by_condition <- by(data = data$wpm, INDICES = data$condition, FUN = sd) %>%
  rbind() %>%
  as_tibble()

```


* Mean:
  + For the `r colnames(mean_wpm_by_condition[1])` users have  a `mean` of `r mean_wpm_by_condition[[1]]` *wpms*,  for`r colnames(mean_wpm_by_condition[2])` a `mean` of `r   mean_wpm_by_condition[[2]]`    *wpms* and  for`r colnames(mean_wpm_by_condition[3])` has a `mean` of `r mean_wpm_by_condition[[3]]` *wpms*.

* Spread:
  + For the variance (`var`), `r colnames(min_wpm_by_condition[1])` has a value of `r var_wpm_by_condition[[1]]`, `r colnames(var_wpm_by_condition[2])` has a value of `r var_wpm_by_condition[[2]]` and  `r colnames(var_wpm_by_condition[3])` has a value of `r var_wpm_by_condition[[3]]`.
  + Regarding the standard deviation, (`sd`) `r colnames(sd_wpm_by_condition[1])` accounts to `r sd_wpm_by_condition[[1]]`, `r colnames(sd_wpm_by_condition[2])` to `r sd_wpm_by_condition[[2]]` and `r colnames(sd_wpm_by_condition[3])` to `r sd_wpm_by_condition[[3]]`.
  
  
  
  
  
  